Fast Fourier transformation of electromagnetic data for computationally expensive kernels

### 2021-02-27 ManuscriptTime.tex
land ip

@@

>>>>

\rtodo 1 \added{\emph{The independence from spatial model complexity is in my
  opinion debatable, because of a potential issue with the accuracy of phase
  information. It’s my experience that a high degree of imaginary-field
  component accuracy is needed for a proper f-t transform. --
  I also needed a high level of numerical accuracy in the f-domain, that is,
  very fine meshes and tight solver tolerances. An aspect which in my opinion
  is not addressed sufficiently in the current manuscript.}: Add somewhere that
  high accurate results are required}.

\rtodo 2 \added{\emph{In my first revision, I actually did not make a request
  for making the literature review "more extensive". Instead, I wrote that the
  authors "should spend more time researching the EM literature that is related
  to the actual topic." As it was and still is, half of the introduction
  (current manuscript, page 2 to p. 3, line 46) is a rather broad/general EM
  overview. Given the fact that the paper connects directly to Plessix et al.
  (2007) and Mulder et al. (2008), I would have expected a more targeted
  introduction towards the specific advances of this manuscript – instead of
  talking about a choice of only loosely connected and more general topics like
  Lebedev grids, tetrahedral grids, integral equation, direct solvers, etc. I
  like that the introduction is generally concise. My impression remains that
  the introduction can have the same length but be more targeted. Other readers
  may also see it that way. I won’t need another explanation about your
  potentially differing opinion. This is just a suggestion for improvement.
  Feel free to ignore.}}

\rtodo 3 Reply; Include comments from earlier review; papers that were
referred; difficulties in late/early times; IP effects. Refer to steel-casing
effects (lindsey), but state we look here at non-Debye cole models.
Add also the papers seogi mentioned re IP effects.
\emph{We tried to improve the introduction and focus more on the actual topic.
  Amongst other, we address the topic of steel casing and non-Debye Cole-Cole
models.}

@@

for c>0.6, 17 frequencies from 1.2e-4 to 8.3\,Hz would be sufficient.

%    'src': (0, 0, 0.01),
%    'rec': (900, 0, 0.01),
%    'depth': [0, 300, 400],
%    res = 2e14, 1, 1, 1
%    layer: cond_8 = 1.25, cond_0 = 1 => m = 0.2
%    tau: 1
%    fmin=1e-4,
%    fmax=5e2,
%    signal=1,        # <= Step-On!
%    every_x_freq=6,  # Only every 6th value

%  time        [s] :  0.01 - 10000 : 301  [min-max; #]
%  Fourier         :  DLF (Sine-Filter)
%    > Filter      :  Key 601 CosSin (2009)
%    > DLF type    :  Lagged Convolution
%  Req. freq  [Hz] :  6.67463E-18 - 4.00754E+13 : 747  [min-max; #]
%  Calc. freq [Hz] :  0.000155601 - 424.87 : 27  [min-max; #]

% Comparison: Full DLF; cosine-filter step-off, 747 frequencies
% Our method: 27 freqs; DC(no IP) - step-on; DC at 1000 s
%    (no more frequencies were required)
%    important to see that the DC value (low freq, late t; is the same IP/noIP)

The actual transform was carried out with the 601-point sine-cosine filter from
\cite{GEO.09.Key}.

Key 601\,pt filter is very long; seems to be by far the best for low c values.
Designing a new filter specific for IP problems might be the best approach

DC: 1000s; the same amount of frequencies is required to compute times up to
10s or up to 1000s

\cite{GJI.17.Commer}

\begin{itemize}
  \item Designing a DLF for IP effects
  \item DC value is the same for the IP or non-IP model, so one could use
    the non-IP response and do interpolation
\end{itemize}
